Viscous Erosion in Porous Media

### 2018-03-13 docs/methods/erosion_methods.tex
NM

>>>>

In Fig.~\ref{fig:mbodyplots} we also plot the same quantities for the 50-body simulation that was shown in Fig.~\ref{fig:50bodies} of the introduction. Overall, these plots support the same trends seen in the 6-body simulation. The initial area-fraction of the 50-body simulation is only slightly higher, about 45\%, and this fraction decreases steadily as bodies erode. The flow rate $\umax$ again increases very rapidly with time, though with a significantly smaller initial value due to the higher resistance provided by 50 bodies. As before, the total drag remains relatively constant throughout most of the simulation and then abruptly decreases to zero in the final moments. Our measure of resistance, $F_D/(4 \pi \umax)$, again decreases very rapidly in the early moments when channels are initially formed. Though the area fractions of the two simulations are nearly the same, the 50-body configuration provides about 5 times more resistance.
